Improved Bounds for Online Balanced Repartitioning

### 2020-04-24 paper/disc20clustering.tex
Comments

Missing:
\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist? 
\mahmoud{added remark for this case: $t''=0$}}
\maciek{But t' might not exist (as it might be the first collocation).}

Minor:
\maciek{"It can be easily verified"... True, but avoid such formulation. Something along these lines: if opt migrates earlier than t', then additionally pays for X, if later than Y.}
\maciek{"Thus, OPT pays ... which gives the competitive ratio" It is too early to give the competitive ratio if in the next paragraph we consider yet another case. \mahmoud{done!}}

Tiny:
\maciek{$\sigma_t$ undefined (I know what it is, though). \mahmoud{added inline def. Do we have a global def for this?}}
\maciek{Not yet, but we still must write the "Problem definition" section (yes, we don't have one!), and we can put it there.}

\maciek{Define $C^t$ to use once \mahmoud{already defined! I don't get it.}}
\maciek{discussed}

>>>>

Missing:
\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist? 
\mahmoud{added remark for this case: $t''=0$
\maciek{But t' might not exist (as it might be the first collocation).}}}

Minor:
\maciek{"It can be easily verified"... True, but avoid such formulation. Something along these lines: if opt migrates earlier than t', then additionally pays for X, if later than Y.}

Tiny:
\maciek{$\sigma_t$ undefined (I know what it is, though). \mahmoud{added inline def. Do we have a global def for this?}
\maciek{Not yet, but we still must write the "Problem definition" section (yes, we don't have one!), and we can put it there.}}

\maciek{Define $C^t$ to use once \mahmoud{already defined! I don't get it.
\maciek{discussed}}}
